Testing the Relationship between Phenomenological Control related to Illusion Sensitivity

### 2025-03-24 paper/R1/manuscript.qmd
minor

output: officedown::rdocx_document

@@

question <- c("Question", "Hypothesis", "Sampling Plan", "Analysis Plan", "Rationale for Deciding the Sensitivity of the Test", "Interpretation Given Different Outcomes", "Theory That Could Be Shown Wrong by the Outcomes")
answer <- c("Is there a correlation between trait phenomenological control (PC) and visual illusion (VI) sensitivity?", "Replicating findings from Lush et al., 2022 paper, we expect evidence of favour of an absence of relationship between VI and PCS", "The goal is to recruit around 500 adult English speakers using Prolific. This sample size is based on the ones used in Lush et al., 2021 and Lush et al., 2022 that we aim at replicate.", "Bayesian correlations between the PC score and the VI performance for the 3 illusion types (corresponding to the error rate) will be computed using the BayesFactor::BFCorrelation() function (with the r-scale prior parameter set to ‘medium’)", "Evidence against a relationship between PC and VI will be found if BF10 <= 1/3, following the Lush et al., 2022 findings. BF10 > 3 will be interpreted as evidence for a relationship between these two measures.", "The hypothesis that VI sensitivity is independent from PC.", "The cognitive impenetrability of illusions, implying that the effect is driven by low-level processes and therefore not influenced by top-down mechanisms such as PC.")

>>>>

@@

question <- c("Question", "Hypothesis", "Sampling Plan", "Analysis Plan", "Rationale for Deciding the Sensitivity of the Test", "Interpretation Given Different Outcomes", "Theory That Could Be Shown Wrong by the Outcomes")
answer <- c("Is there a correlation between trait phenomenological control (PC) and visual illusion (VI) sensitivity?", "Replicating findings from Lush et al., 2022 paper, we expect evidence to support the absence of a relationship between VI and PCS", "The goal is to recruit around 500 adult English speakers using Prolific. This sample size is based on the ones used in Lush et al., 2021 and Lush et al., 2022 that we aim at replicate.", "Bayesian correlations between the PC score and the VI performance for the 3 illusion types (corresponding to the error rate) will be computed using the BayesFactor::BFCorrelation() function (with the r-scale prior parameter set to ‘medium’)", "Evidence against a relationship between PC and VI will be found if BF10 <= 1/3, following the Lush et al., 2022 findings, for all three illusions. BF10 > 3 will be interpreted as evidence for a relationship between these two measures.", "The hypothesis that VI sensitivity is independent from PC.", "The cognitive impenetrability of illusions, implying that the effect is driven by low-level processes and therefore not influenced by top-down mechanisms such as PC.")
